---
title: "W_UP_01"
author: "Andrew Arredondo"
date: "9/3/24"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

Push ups is numerical 

Position is categorical 

We used the numerical ~ categorical helper file

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->
```{r}
boxplot(pushups~position,data=mydata)
```


## Descriptive Results

In the graph shown above it shows that skill did more pushups then the line. 

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->








  
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
The minimum for pushups for skill was 18 compared to the line which was 6. The max was 108 for skill and line max was 34 which is a huge difference which results in the medians to have a 33 difference between the two positions.


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```


I would have to say it is a HA because there is a significant Difference between the two positions the mean in the line group is 17.13 and in the skill group it is 49.73, The pre-value is 9.4.  




# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Yes there is a relationship if the pushups are low it is related to the line if the pushups are higher it is related to the skill position based off the graphs. My answer is that it is a alternative hypothesis (ha) because it states the the lines pushups are significantly different then skilled position.




